MSDi for all families together

### 2016-04-09 AllFamilys.Rmd
cambios 09/04/2016

---
title: "AllFamilys"
author: "mlm"
date: "20 de marzo de 2016"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE)
```

@@

# Create matrix.
theo.MSDi.nsF = c()
theo.MSDi.nsT = c()
theo.MSDi.nsF.s = c()
theo.MSDi.nsT.s = c()

@@

# Dirs.
out.dir <- "OUT"

@@

print(input)

for (a in (1:nrow(input))) { 
  family <- as.character(input$family)[a]
  p.ref <- as.character(input$p.ref)[a]
  mut.model = input$mut.model[a]
  n.mut.p = input$n.mut.p[a]
  R0 = input$R0[a]
  K.analysis = input$K.analysis[a]

@@

  # ns = F.
  m.nsF.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
  m.nsF.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
  nsF.cF.theo.MSDi = colMeans(m.nsF.cF.theo.dr.squarei, na.rm = T)
  nsF.cF.theo.smooth.MSDi = colMeans(m.nsF.cF.theo.smooth.dr.squarei, na.rm = T)

  # ns = T.
  analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "TRUE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")

  m.nsT.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
  m.nsT.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))
  nsT.cF.theo.MSDi = colMeans(m.nsT.cF.theo.dr.squarei, na.rm = T)
  nsT.cF.theo.smooth.MSDi = colMeans(m.nsT.cF.theo.smooth.dr.squarei, na.rm = T)

  ## Fits.
  fit.nsF.cF = lm(cF.exp.MSDi ~ nsF.cF.theo.MSDi)
  MSDi.fit.nsF.cF = fitted.values(fit.nsF.cF)

  fit.nsT.cF = lm(cF.exp.MSDi ~ nsT.cF.theo.MSDi)
  MSDi.fit.nsT.cF = fitted.values(fit.nsT.cF)

  fit.nsF.cF.s = lm(cF.exp.MSDi.s ~ nsF.cF.theo.smooth.MSDi)
  MSDi.fit.nsF.cF.s = fitted.values(fit.nsF.cF.s)

  fit.nsT.cF.s = lm(cF.exp.MSDi.s ~ nsT.cF.theo.smooth.MSDi)
  MSDi.fit.nsT.cF.s = fitted.values(fit.nsT.cF.s)

  # Concatenate information.
  theo.MSDi.nsF = c(theo.MSDi.nsF, MSDi.fit.nsF.cF)
  theo.MSDi.nsT = c(theo.MSDi.nsT, MSDi.fit.nsT.cF)
  theo.MSDi.nsF.s = c(theo.MSDi.nsF.s, MSDi.fit.nsF.cF.s)
  theo.MSDi.nsT.s = c(theo.MSDi.nsT.s, MSDi.fit.nsT.cF.s)

@@

  exp.MSDi = c(exp.MSDi, cF.exp.MSDi)
  exp.MSDi.s = c(exp.MSDi.s, cF.exp.MSDi.s)

}

# Caluclate measures.
R2.nsF.cF = cor(theo.MSDi.nsF, exp.MSDi)^2 
R2.nsT.cF = cor(theo.MSDi.nsT, exp.MSDi)^2

R2.nsF.cF.s = cor(theo.MSDi.nsF.s, exp.MSDi.s)^2
R2.nsT.cF.s = cor(theo.MSDi.nsT.s, exp.MSDi.s)^2

MSE.nsF.cF = mean((theo.MSDi.nsF - exp.MSDi) ^ 2)
MSE.nsT.cF = mean((theo.MSDi.nsT - exp.MSDi) ^ 2)

MSE.nsF.cF.s = mean((theo.MSDi.nsF.s - exp.MSDi.s) ^ 2)
MSE.nsT.cF.s = mean((theo.MSDi.nsT.s - exp.MSDi.s) ^ 2)

@@

plot(theo.MSDi.nsF, type="l", xlab = "sitio", ylab = "Theoretical")
plot(exp.MSDi, type="l", col ="red", ylab = "Experimental")
plot(theo.MSDi.nsF, type="l", ylab = "both")
points(exp.MSDi, col = "red", type="l")
legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")

@@

```{r, include = F}
layout(matrix(1:3, 3, 1, byrow = F)) 
plot(theo.MSDi.nsT, type="l", xlab = "sitio", ylab = "Theoretical")
plot(exp.MSDi, type="l", col ="red", ylab = "Experimental")
plot(theo.MSDi.nsT, type="l", ylab = "both")
points(exp.MSDi, col = "red", type="l")
legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
```
All familys fitted smooth MSD profiles

@@

```{r}
layout(matrix(1:3, 3, 1, byrow = F)) 
plot(theo.MSDi.nsF.s, type="l", xlab = "sitio", ylab = "Theoretical ns = F")
plot(exp.MSDi.s, type="l", col ="red", ylab = "Experimental")
plot(theo.MSDi.nsF.s, type="l", ylab = "both")
points(exp.MSDi.s, col = "red", type="l")
legend("topleft", paste("R^2", round(R2.nsF.cF.s, digits = 2), " ", "MSE", signif(MSE.nsF.cF.s, digits = 2)), bty = "n", text.col = "red")

@@

```{r}
layout(matrix(1:3, 3, 1, byrow = F)) 
plot(theo.MSDi.nsT.s, type="l", xlab = "sitio", ylab = "Theoretical ns = T")
plot(exp.MSDi.s, type="l", col ="red", ylab = "Experimental")
plot(theo.MSDi.nsT.s, type="l", ylab = "both")
points(exp.MSDi.s, col = "red", type="l")
legend("topleft", paste("R^2", round(R2.nsT.cF.s, digits = 2), " ", "MSE", signif(MSE.nsT.cF.s, digits = 2)), bty = "n", text.col = "red")

>>>>

---
title: "MSDi for all families together"
author: "Maria Laura Marcos"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE)
```

@@

# Directories.
out.dir <- "OUT"

# Create matrixes.
nsF.theo.MSDi = c()
nsT.theo.MSDi = c()
nsF.theo.MSDi.s = c()
nsT.theo.MSDi.s = c()

@@

@@

# Print the input in the html file.
print(input)

# Start a loop to read data for each family.
for (a in (1:nrow(input))) { 
  family <- as.character(input$family)[a]
  mut.model = input$mut.model[a]
  R0 = input$R0[a]
  K.analysis = input$K.analysis[a]

@@

  # natural selection (ns) = F.
  m.nsF.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
  m.nsF.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))

  nsF.cF.theo.MSDi = colMeans(m.nsF.cF.theo.dr.squarei, na.rm = T)
  nsF.cF.theo.MSDi.s = colMeans(m.nsF.cF.theo.smooth.dr.squarei, na.rm = T)

  # natural selection (ns) = T.
  analysis.fname.id <- paste(family, "_mut.model_", mut.model, "_naturalSelection_", "TRUE", "_R0_", R0, "_core_", "FALSE", "_K.analysis_", K.analysis, sep = "")

  m.nsT.cF.theo.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.dr.squarei.csv", sep = "")))
  m.nsT.cF.theo.smooth.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.dr.squarei.csv", sep = "")))

  nsT.cF.theo.MSDi = colMeans(m.nsT.cF.theo.dr.squarei, na.rm = T)
  nsT.cF.theo.MSDi.s = colMeans(m.nsT.cF.theo.smooth.dr.squarei, na.rm = T)

  ## Fit theoretical data with experimental data.
  fit.nsF.cF = lm(cF.exp.MSDi ~ nsF.cF.theo.MSDi)
  fit.nsF.cF.MSDi = fitted.values(fit.nsF.cF)

  fit.nsT.cF = lm(cF.exp.MSDi ~ nsT.cF.theo.MSDi)
  fit.nsT.cF.MSDi = fitted.values(fit.nsT.cF)

  fit.nsF.cF.s = lm(cF.exp.MSDi.s ~ nsF.cF.theo.MSDi.s)
  fit.nsF.cF.MSDi.s = fitted.values(fit.nsF.cF.s)

  fit.nsT.cF.s = lm(cF.exp.MSDi.s ~ nsT.cF.theo.MSDi.s)
  fit.nsT.cF.MSDi.s = fitted.values(fit.nsT.cF.s)

  # Concatenate information.
  nsF.theo.MSDi = c(nsF.theo.MSDi, fit.nsF.cF.MSDi)
  nsT.theo.MSDi = c(nsT.theo.MSDi, fit.nsT.cF.MSDi)
  nsF.theo.MSDi.s = c(nsF.theo.MSDi.s, fit.nsF.cF.MSDi.s)
  nsT.theo.MSDi.s = c(nsT.theo.MSDi.s, fit.nsT.cF.MSDi.s)

@@

  exp.MSDi = c(exp.MSDi, cF.exp.MSDi)
  exp.MSDi.s = c(exp.MSDi.s, cF.exp.MSDi.s)
}

# Caluclate measures.
R2.nsF.cF = cor(nsF.theo.MSDi, exp.MSDi) ^ 2 
R2.nsT.cF = cor(nsT.theo.MSDi, exp.MSDi) ^ 2

R2.nsF.cF.s = cor(nsF.theo.MSDi.s, exp.MSDi.s) ^ 2
R2.nsT.cF.s = cor(nsT.theo.MSDi.s, exp.MSDi.s) ^ 2

MSE.nsF.cF = mean((nsF.theo.MSDi - exp.MSDi) ^ 2)
MSE.nsT.cF = mean((nsT.theo.MSDi - exp.MSDi) ^ 2)

MSE.nsF.cF.s = mean((nsF.theo.MSDi.s - exp.MSDi.s) ^ 2)
MSE.nsT.cF.s = mean((nsT.theo.MSDi.s - exp.MSDi.s) ^ 2)

@@

plot(nsF.theo.MSDi, type = "l", xlab = "sitio", ylab = "Theoretical")
plot(exp.MSDi, type = "l", col = "red", ylab = "Experimental")
plot(nsF.theo.MSDi, type = "l", ylab = "both")
points(exp.MSDi, col = "red", type = "l")
legend("topleft", paste("R^2", round(R2.nsF.cF, digits = 2)), bty = "n", text.col = "red")

@@

```{r, include = F}
layout(matrix(1:3, 3, 1, byrow = F)) 
plot(nsT.theo.MSDi, type="l", xlab = "sitio", ylab = "Theoretical")
plot(exp.MSDi, type="l", col ="red", ylab = "Experimental")
plot(nsT.theo.MSDi, type="l", ylab = "both")
points(exp.MSDi, col = "red", type="l")
legend("topleft", paste("R^2", round(R2.nsT.cF, digits = 2)), bty = "n", text.col = "red")
```
All families fitted smooth normalized MSD profiles

@@

```{r}
plot(nsF.theo.MSDi.s, type = "l", xlab = "sitio", ylab = "Theoretical ns = F", ylim = c(0, 0.14))
```

```{r}
plot(exp.MSDi.s, type = "l", col = "red", ylab = "Experimental", ylim = c(0, 0.14))
```

```{r}
plot(nsF.theo.MSDi.s, type = "l", ylab = "both", ylim = c(0, 0.14))
points(exp.MSDi.s, col = "red", type = "l")
legend("topleft", paste("R^2", round(R2.nsF.cF.s, digits = 2), " ", "MSE", signif(MSE.nsF.cF.s, digits = 4)), bty = "n", text.col = "red")
```

@@

```{r}
plot(nsT.theo.MSDi.s, type="l", xlab = "sitio", ylab = "Theoretical ns = T", ylim = c(0, 0.14))
```

```{r}
plot(exp.MSDi.s, type = "l", col = "red", ylab = "Experimental", ylim = c(0, 0.14))
```

```{r}
plot(nsT.theo.MSDi.s, type = "l", ylab = "both", ylim = c(0, 0.14))
points(exp.MSDi.s, col = "red", type = "l")
legend("topleft", paste("R^2", round(R2.nsT.cF.s, digits = 2), " ", "MSE", signif(MSE.nsT.cF.s, digits = 2)), bty = "n", text.col = "red")
```
